%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\textbf{\Huge \scshape Arjun Sarao}} \\ \vspace{1pt}
     \href{mailto:arjun.sarao@uwaterloo.ca}{\underline{arjun.sarao@uwaterloo.ca}} $|$ 
    \href{https://www.linkedin.com/in/arjun-sarao-bb555b1b4/}{\underline{linkedin.com/in/arjun-sarao}} $|$
    \href{https://github.com/DarkHawk727}{\underline{github.com/DarkHawk727}}
\end{center}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full Stack Web Developer}{May 2022 -- December 2022}
      {Starai Tutoring}{}
      \resumeItemListStart
        \resumeItem{Designed and wire-framed a responsive, multi-page static website based on client specifications in \textbf{Figma}.}
        \resumeItem{Developed the website using \textbf{JavaScript (React.js)} in conjunction with
        \textbf{Bulma.css}, hosted it on \textbf{GitHub Pages}.}
        \resumeItem{Implemented sign-up form submission via \textbf{Firebase} cloud-function and SMS notifications with \textbf{Twilio}.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Deep Work Tracker} $|$ \emph{Web-App for Productivity Tracking.}}{September 2023}
          \resumeItemListStart
                \resumeItem {Scripted and deployed application interface using \textbf{Streamlit}.}
                \resumeItem {Added metrics such as time between accomplishments, churn-rate, and activity graph}
                \resumeItem {Stored data in \textbf{Supabase}, created custom \textbf{SQL} commands to query, integrated with \textbf{Python} client.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Personal AI} $|$ \emph{LLM-Powered Web-app for University Help.}}{August 2023}
          \resumeItemListStart
                \resumeItem {Created  and deployed a multi-page front-end using \textbf{Streamlit}.}
                \resumeItem {Integrated \textbf{GPT-4} via \textbf{LangChain} to provide enhanced, domain-specific, knowledge such as PDF Q\&A, Flashcard Generation, and Math Help via \textbf{sympy}.}
                \resumeItem{Augmented retrieval with \textbf{chromadb} to store text embeddings on disk to save repeat costs and add additional context to queries.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Philosopedia} $|$ \emph{AI-powered Flutter app for Stanford Encyclopedia of Philosophy.}}{August 2023}
          \resumeItemListStart
                \resumeItem {Created and wireframed UX using \textbf{Figma}, Developed \textbf{Flutter (Dart)} application with use of \textbf{RapidAPI} for content aggregation.}
                \resumeItem {Rendered text in frontend using \textbf{bionic-reading}.}
                \resumeItem {Passed entry preamble to \textbf{HuggingFace} (BART) for summarization and then onto \textbf{OpenAI's GPT-4} for question generation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Science (CO-OP)}{University of Waterloo}
      {}{Sept. 2022 -- present}
      \resumeItemListStart
      \resumeItem{Member of the Badminton, Computer Science, and Data Science Clubs.}
      \resumeItem{Awarded the President's Scholarship.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SELF LEARNING----------------
\section{Self Learning}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Learn Deep Learning for Coders with fastai and PyTorch}}{Present}
          \resumeItemListStart
              \resumeItem {Programming exercises designed to teach \textbf{PyTorch}, \textbf{NumPy}, \textbf{Pandas}, \textbf{Matplotlib}, and \textbf{fastai}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Machine Learning Specialization} $|$ \emph{Coursera}}{August 2022}
          \resumeItemListStart
                \resumeItem {Supervised Machine Learning: Regression and Classification (\textbf{Linear Regression, Logistic Regression})}
                \resumeItem {Advanced Learning Algorithms (\textbf{Neural Networks, Decision Trees})}
                \resumeItem {Unsupervised Learning, Recommenders, Reinforcement Learning (\textbf{Clustering, Anomaly Detection, Collaborative Filtering, Deep Q-Learning})}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Deep Learning Specialization} $|$ \emph{Coursera}}{July 2022}
          \resumeItemListStart
                \resumeItem {Neural Networks and Deep Learning (\textbf{NNs})}
                \resumeItem {Improving Deep Neural Networks: Hyperparameter Tuning, Regularization, and Optimization}
                \resumeItem {Convolutional Neural Networks (\textbf{CNNs})}
                \resumeItem {Sequence Models (\textbf{RNNs, GRUs, LSTMs, Transformer Networks})}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PERSONAL ACHIEVMENTS-----------
\section{Personal Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Cadets}{: Appointed Regulating Petty Officer, Obtained CanSail 1\&2, achieved rank of Chief Petty Officer 2nd Class} \\
     \textbf{Sports}{: Represented school at city and district levels for badminton and swimming.} \\
     \textbf{Hackathons}{: 2x Google Cloud Prize Recipient (\emph{UncommonHacks, Hack-o-Lantern}), 1st place People's Choice (\emph{WinHacks 2021}), Best Theme Hack (\emph{PreHackstoric}) } \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
